---
title: "W_UP_01"
author: "Anthony Falconio"
date: "fall 2023"
output: html_document
---



The report structure should include five sections.  see below



```{r include=TRUE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r include=TRUE,echo=FALSE}
ggplot(data = mydata, aes(x = pushups, y = position)) +
  geom_boxplot() +
  labs(title = "Pushups by position", x = "Pushups", y = "Position") +
  coord_flip() +
  theme(plot.title = element_text(size = 18, hjust = 0.5)) # Adjust title size and position
```

  
The data from the box plot shows that skilled position players are able to perform more pushups than line position players. 

This can be inferred from the box plot with the left column representing line positions, and the right column representing skilled positions. 

The higher height of the skilled position box indicates that skilled players are doing considerably more pushups than line players.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```

The average number of pushups that a line player can perform is about a third of the average number of pushups that a skill player can perform.

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
t.test(pushups~position,data=mydata)
```
p-value = 0.000009421

The p-value is far smaller than 0.05 indicated that there is a strong statistical significance. This rejects the $H_O$ leaving only the $H_A$

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

$H_0$ = there is no difference in pushups based on position
$H_A$ = there is a difference in pushups based on position

With the help of ChatGPT, I was able to write and organize the R code to create a box plot representing the difference in pushups performed between two different positions of players. I was also able to perform a T test using the Numerical-Cat tool with a summary of data under favstats. The results of the T test shows that we can reject the $H_O$ only leaving the $H_A$ to be true.